Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-09 analysis/output/figures/hypotheses/Hypotheses.Rmd
Added age and race plots

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

>>>>

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
    # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
      covariates == c( "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
    str_c(
      "Medium to follow news: ", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    ),
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No")) %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

### 2019-10-09 manuscript/manuscript.Rmd
Added age and race plots

The following plots zoom in on the strength of the effects that these characteristics have.

@@

  ![](output/figures/demographics.png)
  - `Donation preferences ~ (Public affairs) + (Political ideology)`

>>>>

The following plots zoom in on the strength of the effects of these characteristics.

@@

  ![](output/figures/demographics.png)
    - Gender

    - Marital Status
  ![](output/figures/marital-status.png)  
  Question: it seems that levels like emergency response are omitted because they're considered the base to compare to. Why is there not a "Marital status: Married" though? It can't be the same thing

  - Education
  ![](output/figures/education.png)
    - Income
  ![](output/figures/income.png)
    - Race 
    ![](output/figures/race.png)
    - Age 
  ![](output/figures/age.png)

  - `Donation preferences ~ (Public affairs) + (Political ideology)`
